---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
devtools::load_all()
```

# broadcast

<!-- badges: start -->

<!-- badges: end -->

The R package `broadcast` provides [numpy](https://numpy.org/doc/stable/index.html) style [broadcasting](https://numpy.org/doc/stable/user/basics.broadcasting.html) ability to R matrices (not yet on arrays more than 2D!).

```{r, eval = FALSE}
# remotes::install_github("talegari/broadcast") # not (yet) on CRAN
library("broadcast")
```

```{r, error = TRUE}
m1 = matrix(1:6, nrow = 2)
m1

m2 = matrix(7:9, nrow = 1)
m2

# without `broadcast`
m1 + m2

# with `broadcast`
m1 %a+% m2
```

## What's inside

-   `%a+%` (aka `array_add`)
-   `%a-%` (aka `array_sub`)
-   `%a*%` (aka `array_mul`)
-   `%a/%` (aka `array_div`)
-   `array_pairwise` : Apply any function operating pairwise
-   `is_broadcastable`: Whether a matrix or a dimension can be broadcasted to a new dimension
-   `get_pairwise_broadcast_dim`: Common broadcastable dimension given a pair of matrices
-   `broadcast_to`: broadcast a matrix to a given dimension

## Caveats

1.  Written in R, not C++ (still plenty fast!)
2.  Works only on matrices and not generalized to arrays (as of now)
3.  Won't go on CRAN until (1) an (2) are resolved :)

## Installation

```         
remotes::install_github("talegari/broadcast")
```

------------------------------------------------------------------------

```         
ನರಕಕ್ಕ್ ಇಳ್ಸಿ ನಾಲ್ಗೆ ಸೀಳ್ಸಿ
ಬಾಯ್ ಒಲಿಸಾಕಿದ್ರೂನೆ-
ಮೂಗ್ನಲ್ ಕನ್ನಡ್ ಪದವಾಡ್ತೀನಿ!
```

[ರತ್ನನ್ ಪದಗಳು.](https://sites.google.com/site/kavanasangraha/%E0%B2%95%E0%B2%B5%E0%B2%A8-%E0%B2%B8%E0%B2%97%E0%B2%B0%E0%B2%B9/%E0%B2%9C-%E0%B2%AA-%E0%B2%B0%E0%B2%9C%E0%B2%B0%E0%B2%A4%E0%B2%A8/%E0%B2%B0%E0%B2%A4%E0%B2%A8%E0%B2%A8-%E0%B2%AA%E0%B2%A6%E0%B2%97%E0%B2%B3)
